---
title: "Analyis of Presto from Bach Sonata No 1"
author: "K.G."
date: '2020-04-09'
output:
  pdf_document: default
  html_document: default
---

<style>
   tbody tr:nth-child(odd){
    background-color: #FFFFFF;
  }
</style>



```{r, echo=T, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(repos="https://cran.rstudio.com" )


requirements <- c("caret","lattice", "scatterplot3d", "ResourceSelection", "car", "corrplot", "smacof", "MASS", "CCA", "CCP", "GGally", "reshape2", "ggplot2", "MVN", "mvnormtest", "mclust", "vcd", "cluster", "rpart", "Hmisc", "foreign", "neuralnet", "fpc", "MTS", "plotly", "Rcpp", "ggvis", "googleVis", "rCharts", "plotly", "dplyr", "tidyr", "knitr","mclust","tsintermittent","GGally","ggplot2","scales","tictoc","dynlm","PerformanceAnalytics","stargazer","tseries","forecast","zoo","quantmod","dplyr","ggplot2","tidyr","scales","chron","stringr","gdata","zoo","lmtest","stringr","plyr","dplyr","data.table","lubridate","ggplot2","rmarkdown","knitr","kableExtra","forecast","prophet","zoo","openxlsx","tidyverse","tictoc","CombMSC","bsts","Rcpp","RColorBrewer","ggpubr","Metrics", "here")
for(requirement in requirements){
  if( !(requirement %in% installed.packages())) {
    #print(requirement)
    install.packages(requirement)
    }
  }
lapply(requirements, require, character.only=T)

merge.all.CM.aff = function(x,y){
  merge(x,y,by = c("CM"),all = T)

}
base_dir = here::here()
setwd(base_dir)
library(kableExtra)

subDir = "results"
dir.create(file.path(base_dir, subDir), showWarnings = FALSE)

mycolor.pink = c("#ffe9ec","#ffd0d7","#ffb6c1","#ff9dab","#ff8396","#ff6a80","#ed1556")
mycolor.lavender = c("#e6e6fa","#d9d9fc","#c4c4fc","#acacfe","#9696fe")

mycolor.blue = c("#003c3f","turquoise4","#00b7be","darkturquoise", "#81D8D0","aquamarine","paleturquoise1","lightskyblue1", "cornflowerblue","royalblue1","dodgerblue3","mediumblue","navy","midnightblue","#0a0a2c")

library(readxl)

#' Read multiple tabs in excel spreadsheet (`read_excel_allsheets`)
#' @input filename: name of file
#' @output output a list of files

read_excel_allsheets <- function(filename, tibble = FALSE) {
  # I prefer straight data.frames
  # but if you like tidyverse tibbles (the default with read_excel)
  # then just pass tibble = TRUE
  sheets <- readxl::excel_sheets(filename)
  x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
  if(!tibble) x <- lapply(x, as.data.frame)
  names(x) <- sheets
  x
}



```

## Load Data
```{r, echo=T, warning=FALSE, message = FALSE,fig.align="center", fig.height=7, fig.width=4}
df_presto_raw = read_excel_allsheets("PRESTO ANALYSIS Part II.xlsx")$Sheet1
tests_names <- paste0("Test", seq(1:9))
formula = paste0(tests_names, collapse = "+")
df_presto_calc <- as.data.table(df_presto_raw)
string_execute <- paste0("df_presto_calc[, Num_of_Flag := ",formula,"]")
eval(parse(text = string_execute))

df_presto_melt <- melt(df_presto_raw, id.vars = c("Bar ID","String_Crossing_One_Bow","String_Crossing_Space_String","Position_Shifting","Left_Out_Note"))
```

## Summary by Bar
```{r, echo=T, warning=FALSE, message = FALSE,fig.align="center", fig.height=7, fig.width=10}
df_gg_by_bar <- df_presto_melt %>% 
  
  dplyr::mutate(   NUM_String_Crossing_One_Bow = ifelse(String_Crossing_One_Bow == "T", value, 0),
                   NUM_String_Crossing_Space_String = ifelse(String_Crossing_Space_String == "T", value, 0),
                   NUM_Position_Shifting = ifelse(Position_Shifting == "T", value, 0),
                   NUM_Left_Out_Note = ifelse(Left_Out_Note == "T", value, 0)) %>% 
  dplyr::group_by(`Bar ID`) %>% 
  dplyr::summarise(Total_error = sum(value),
                   String_Crossing_One_Bow = sum(NUM_String_Crossing_One_Bow),
                   String_Crossing_Space_String = sum(NUM_String_Crossing_Space_String),
                   Position_Shifting = sum(NUM_Position_Shifting),
                   Left_Out_Note = sum(NUM_Left_Out_Note)) %>% 
  melt(id.vars = "Bar ID") %>% 
    as.data.table()

df_gg_by_bar$variable <- as.character(df_gg_by_bar$variable)

 gg_by_bar =  ggplot(df_gg_by_bar,aes(`Bar ID`,value,label = value)) +
    geom_segment( aes(x=`Bar ID`, xend=`Bar ID`, y=0, yend=value), color="grey") +
    geom_point( aes(x=`Bar ID`, y=value), color = "firebrick3", size=4, shape = 19) +
    geom_text(color = "white", size = 2)+
    #coord_flip()+
    theme_light() +
    facet_wrap(~variable, ncol = 1, scales = "fixed")+
    scale_y_continuous( breaks = seq(0,10,2), limits = c(0,10))+ 
    theme(
      plot.title = element_text(size=10,hjust = 0.5),
      legend.position = "none",
      panel.border = element_blank(),
      axis.text=element_text(size=10)) +
    ggtitle("Error Tracker")

print(gg_by_bar)

png("Erro Tracker.png", width = 2000, height = 1500, res=130)
print(gg_by_bar)
dev.off()

```

\newpage

## Test-Based Impact

### String_Crossing_One_Bow

```{r, echo=T, warning=FALSE, message = FALSE,fig.align="center"}
test_String_Crossing_One_Bow <- df_presto_melt %>% 
  dplyr::mutate(r = 1) %>% 
  dplyr::group_by(String_Crossing_One_Bow) %>% 
  dplyr::summarise(fail = sum(value),
                   all = sum(r),
                   success = all- fail)

mat = rbind(test_String_Crossing_One_Bow$success,test_String_Crossing_One_Bow$fail)
row.names(mat) <- c("No String_Crossing_One_Bow", "String_Crossing_One_Bow")
colnames(mat) <-  c("Success","Fail")

fisher.test(mat, alternative="greater")
spine(xtabs(~String_Crossing_One_Bow+value, data=df_presto_melt))

```

\newpage

### String_Crossing_Space_String

```{r, echo=T, warning=FALSE, message = FALSE,fig.align="center"}
test_String_Crossing_Space_String <- df_presto_melt %>% 
  dplyr::mutate(r = 1) %>% 
  dplyr::group_by(String_Crossing_Space_String) %>% 
  dplyr::summarise(fail = sum(value),
                   all = sum(r),
                   success = all- fail)
  

mat = rbind(test_String_Crossing_Space_String$success,test_String_Crossing_Space_String$fail)
row.names(mat) <- c("No String_Crossing_Space_String", "String_Crossing_Space_String")
colnames(mat) <-  c("Success","Fail")

fisher.test(mat, alternative="greater")
spine(xtabs(~String_Crossing_Space_String+value, data=df_presto_melt))

```

\newpage

### Position_Shifting

```{r, echo=T, warning=FALSE, message = FALSE,fig.align="center"}
test_Position_Shifting <- df_presto_melt %>% 
  dplyr::mutate(r = 1) %>% 
  dplyr::group_by(Position_Shifting) %>% 
  dplyr::summarise(fail = sum(value),
                   all = sum(r),
                   success = all- fail)
  

mat = rbind(test_Position_Shifting$success,test_Position_Shifting$fail)
row.names(mat) <- c("No Position_Shifting", "Position_Shifting")
colnames(mat) <-  c("Success","Fail")

fisher.test(mat, alternative="greater")

spine(xtabs(~Position_Shifting+value, data=df_presto_melt))
```

\newpage

### Left_Out_Note

```{r, echo=T, warning=FALSE, message = FALSE,fig.align="center"}
test_Left_Out_Note <- df_presto_melt %>% 
  dplyr::mutate(r = 1) %>% 
  dplyr::group_by(Left_Out_Note) %>% 
  dplyr::summarise(fail = sum(value),
                   all = sum(r),
                   success = all- fail)
  

mat = rbind(test_Left_Out_Note$success,test_Left_Out_Note$fail)
row.names(mat) <- c("No Left_Out_Note", "Left_Out_Note")
colnames(mat) <-  c("Success","Fail")

fisher.test(mat, alternative="greater")



spine(xtabs(~Left_Out_Note+value, data=df_presto_melt))
```

\newpage

## Model-Based Impact

```{r, echo=T, warning=FALSE, message = FALSE,fig.align="center"}
t.ctrl <- caret::trainControl(method = "repeatedcv", 
                       number = 10,
                       savePredictions = TRUE)
tic()
svm.grid <- expand.grid(C = 2^(1:3), sigma = seq(0.25, 2, length = 8))

df_presto_melt_classify <- copy(df_presto_melt)
df_presto_melt_classify$value <- 1-df_presto_melt_classify$value

svm.train <- train(factor(value) ~ String_Crossing_One_Bow + String_Crossing_Space_String + Position_Shifting  + Left_Out_Note,
  data = df_presto_melt_classify, 
  method = "svmRadial",
  trControl = t.ctrl, 
  tuneGrid = svm.grid,
  preProcess = c("center", "scale")
)
# confusionMatrix(svm.predict, factor(df_presto_melt$value))
varImp(svm.train)
toc()
```

## Interaction Terms

Placeholder here for interaction terms where multiple factors impact on the success rate

### String_Crossing_One_Bow + String_Crossing_Space_String

```{r, echo=T, warning=FALSE, message = FALSE,fig.align="center"}
structable(value~ String_Crossing_One_Bow + String_Crossing_Space_String, data = df_presto_melt)
```

### String_Crossing_One_Bow + Position_Shifting

```{r, echo=T, warning=FALSE, message = FALSE,fig.align="center"}
structable(value~ String_Crossing_One_Bow + Position_Shifting, data = df_presto_melt)
```

### String_Crossing_One_Bow + Left_Out_Note

```{r, echo=T, warning=FALSE, message = FALSE,fig.align="center"}
structable(value~ String_Crossing_One_Bow + Left_Out_Note, data = df_presto_melt)
```


### String_Crossing_Space_String + Position_Shifting

```{r, echo=T, warning=FALSE, message = FALSE,fig.align="center"}
structable(value~ String_Crossing_Space_String + Position_Shifting, data = df_presto_melt)
```


### String_Crossing_Space_String + Left_Out_Note

```{r, echo=T, warning=FALSE, message = FALSE,fig.align="center"}
structable(value~ String_Crossing_Space_String + Left_Out_Note, data = df_presto_melt)
```

### Position_Shifting + Left_Out_Note

```{r, echo=T, warning=FALSE, message = FALSE,fig.align="center"}
structable(value~ Position_Shifting + Left_Out_Note, data = df_presto_melt)

```